\documentclass{kththesis}

\usepackage{blindtext} % This is just to get some nonsense text in this template, can be safely removed
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{biblatex}
\usepackage{chngpage}
\usepackage{csquotes} % Recommended by biblatex
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{mwe}
\usepackage{multirow}
\usepackage[parfill]{parskip}
\usepackage{subcaption}

\addbibresource{references.bib} % The file containing our references, in BibTeX format


% --- TITLE & FRONT PAGE ---

\title{Feature Selection Methods for Classification of Breast Cancer}
\alttitle{Attributurvalsmetoder för klassificering av bröstcancer }
\author{Niklas Lindqvist\newline Thony Price}
\email{nlinq@kth.se\newline thonyp@kth.se}
\supervisor{Pawel Herman}
\examiner{Örjan Ekeberg}
\programme{Degree Project in Computer Science}
\school{School of Computer Science and Communication}
\date{\today}


\begin{document}
% Frontmatter includes the titlepage, abstracts and table-of-contents
\frontmatter
\titlepage


% --- ABSTRACT ENGLISH ---

\begin{abstract}

  Breast cancer is the leading cause of cancer deaths among women today but computer aided diagnosis has proved efficient in assisting medical experts to set an early diagnosis improving the chance of recovery. Computer aided diagnostics utilises machine learning to make a prediction whether a patient has a benign or malignant cancer. In the process a patients data is put into machine learning algorithms and a classification is made. Applying feature selection mean algorithms can be fed data with lower dimensionality and produce a more accurate result. We've found classifiers from different disciplines of machine learning all see the benefit of a higher classification accuracy when using feature selection.

\end{abstract}


% --- ABSTRACT SWEDISH ---

\begin{otherlanguage}{swedish}
  \begin{abstract}

  Brostcancer ar idag den ledande cancerformen som orsakar for tidig dod hos kvinnor. Datordriven diagnostisering har visat sig effektiv i att assistera medicinska experter med att satta en tidig diagnos for cancers och darmed oka chanserna for tillfrisknande hos patienten. Datordriven diagnostisering anvander sig av maskininlarningsmetoder for att gora en prediktion huruvida en patient har god eller elakartad cancer. I denna processes anvands en patients data av maskininlarningsalgoritmen och en klassificering kan goras. Applikationen av attributurvalsmetoder innebar att algoritmen kan anvanda sig av data med farre dimensioner och producera ett mer traffsakert resultat. Vi fann att klassificerare fran olika dicipliner av maskininlarning alla visade fordelen med hogre klassificeringstraffsakerhet nar attributurvalsmetoder anvandes.

  \textit{Fix swedish symbols for ao ae oe here...}

  \end{abstract}

\end{otherlanguage}


\tableofcontents
% Mainmatter is where the actual contents of the thesis goes
\mainmatter


% --- CONTENT ---

% --- 1. INTRODUCTION CHAPTER ---
\input{ch1_introduction}

% --- 2. BACKGROUND CHAPTER ---
\input{ch2_background}

% --- 3. METHOD CHAPTER ---
\input{ch3_method}

% --- 4. RESULTS AND ANALYSIS CHAPTER ---
\input{ch4_results}

% --- 5. DISCUSSION ---
\input{ch5_discussion}

% --- 6. CONCLUSION ---
\input{ch6_conclusion}


% --- BIBLIOGRAPHY AND APPENDIX ---

\printbibliography[heading=bibintoc] % Print the bibliography (and make it appear in the table of contents)

\appendix
\chapter{Unnecessary Appended Material}

\end{document}
